A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-04-14 01-intro.tex
Revisão Seção 1

\begin{enumerate}
\item
    Understanding, finding corner cases, and setting compromises.
    After the semantics was complete and discussed in extent, we found a bug in
    the order of execution of statements in a specific case.
\item
    Explaining core aspects of the language in a reduced, precise, and
    unambiguous way.
    This is particularly important when comparing languages that are similar in
    the surface (e.g., \CEU and Esterel).
\item
    Implementing the language.
    Small-step operational semantics typically describe abstract machines that
    are close to concrete implementations.
    The current implementation of the \CEU scheduler is based on the formal
    semantics.
\item
    Proving properties for particular or all programs in the language.
    We prove that all programs in \CEU are memory bounded, deterministic, and
    react in finite time.
\end{enumerate}

The last item is particularly important in the context of embedded systems:

\begin{description}
\item[Memory Boundedness:]
At compile time, we can ensure that the program fits in the device's restricted
memory and that it will not grow unexpectedly during runtime.
\item[Deterministic Execution:]
We can simulate an entire program execution providing an input history with the
guarantee that it will always behave the same.
This can be done in negligible time in a controlled development environment and
with multiple users (e.g., multiple developers each on its desktop) before
deploying the application in the actual device.
\item[Terminating Reactions:]
Real-time applications must guarantee responses within specified deadlines.
A terminating semantics enforces upper bounds for all reactions and guarantees
that programs always progress with the time.
In addition, it also ensures that programs always reach an idle state amenable
to entering in standby mode, which is can improve the autonomy of
battery-powered devices.
\end{description}

>>>>

\begin{enumerate}
\item
    Understanding, finding corner cases, and stabilizing the language.
    After the semantics was complete and discussed in extent in our group, we
    found a critical bug in the order of execution of statements.
\item
    Explaining core aspects of the language in a reduced, precise, and
    unambiguous way.
    This is particularly important when comparing languages that are similar in
    the surface (e.g., \CEU and Esterel).
\item
    Implementing the language.
    A small-step operational semantics describes an abstract machine that is
    close to a concrete implementation.
    The current implementation of the \CEU scheduler is based on the formal
    semantics presented in this paper.
\item
    Proving properties for particular or all programs in the language.
    For instance, in this work, we prove that all programs in \CEU are memory
    bounded, deterministic, and react in finite time.
\end{enumerate}

The last item is particularly important in the context of constrained embedded
systems:

\begin{description}
\item[Memory Boundedness:]
At compile time, we can ensure that the program fits in the device's restricted
memory and that it will not grow unexpectedly during runtime.
\item[Deterministic Execution:]
We can simulate an entire program execution providing an input history with the
guarantee that it will always have the same behavior.
This can be done in negligible time in a controlled development environment
before deploying the application in the actual device (e.g., by multiple
developers in standard desktops).
\item[Terminating Reactions:]
Real-time applications must guarantee responses within specified deadlines.
A terminating semantics enforces upper bounds for all reactions and guarantees
that programs always progress with the time.
%In addition, it also ensures that programs always reach an idle state amenable
%to entering in standby mode, which can improve the autonomy of battery-powered
%devices.
\end{description}
